{ \fontfamily{ptm}\selectfont Catalyst Meta Acceleration Framework: The history and the gist of it }

### 2024-12-10 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

    The theorem looks exciting, but Lin 2015 \cite{lin_universal_2015} page 11 pointed out that $\mathcal G_k^*, \mathcal J_{\lambda_k} y_k$ are both intractable quantities. 

@@

        Next, we show that if $L\delta_k = 1 + \xi_k + \tau_k$ then $v_{k + 1} - x_{k + 1} = (1 + \xi_t)^{-1}\tau_t(x_{k + 1} - x_k)$. 

@@

            L\alpha_{k + 1}\alpha_k^2 - \mu \alpha_k^2 + L \alpha_{k + 1}^2 + \mu\alpha_{k + 1}

@@

                (1 - \alpha_{k + 1})L\alpha_k^2 - \mu\alpha_{k + 1}

@@

    \begin{lemma}[Stationarity condition]\label{app:lemma:ncnvx-catalyst-stationary-cond}
        Assume $F$ is $\rho$ weakly convex. 
        Fix any $y$, suppose that $y^+$ satisfies $\dist(\mathbf 0,\partial \mathcal M^{k^{-1}}(y^+; y)) \le \epsilon$ then the following inequality holds: 
        \begin{align*}
            \dist(\mathbf 0; \partial F(y^+)) 
            \le \epsilon + \kappa\Vert y^+ - y\Vert. 
        \end{align*}
    \end{lemma}
    \begin{proof}
        Take it as a fact that the limiting subgradient of a weakly convex function is a closed set. 
        Fix any $y$, there exists $w \in \partial \mathcal M(y^+; y)$ such that $\dist(\mathbf 0; \partial {\mathcal M}(y^+; y)) = \Vert w\Vert$ because $\partial M(\cdot;y)$ is a $\rho - \kappa$ weakly convex function. 
        Next, by definition we have
        \begin{align*}
            w &\in \partial F(y^+) + \kappa(y^+ - y)
            \\
            \iff 
            \exists v &
            \in \partial  F(y^+): 
            w = v + \kappa(y^+ - y)
            \\
            \implies 
            \epsilon &= 
            \Vert w\Vert = \Vert v + \kappa(y^+ - y)\Vert 
            \ge \Vert v\Vert - \Vert \kappa(y^+ - y)\Vert
            \\
            \implies 
            \dist(\mathbf 0, \partial F(y^+)) &\le 
            \Vert v\Vert 
            \le \epsilon + \Vert \kappa(y^+ - y)\Vert. 
        \end{align*}

>>>>

    The theorem looks exciting, but Lin 2015 \cite{lin_universal_2015} page 11 pointed out that $\mathcal M_k^*, \mathcal J_{\lambda_k} y_k$ are both intractable quantities. 

@@

        Next, we show that if $L\delta_k = 1 + \xi_k + \tau_k$ then $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}\tau_t(x_{k + 1} - x_k)$. 

@@

            L\alpha_{k + 1}\alpha_k^2 - \mu \alpha_k^2 + L \alpha_{k + 1}^2 - \mu\alpha_{k + 1}

@@

                (1 - \alpha_{k + 1})L\alpha_k^2 + \mu\alpha_{k + 1}

@@

    \begin{lemma}[Stationarity condition]\label{app:lemma:ncnvx-catalyst-stationary-cond}
        Assume $F$ is $\rho$ weakly convex. 
        Fix any $y$, suppose that $y^+$ satisfies $\dist(\mathbf 0,\partial \mathcal M^{k^{-1}}(y^+; y)) \le \epsilon$ then the following inequality holds: 
        \begin{align*}
            \dist(\mathbf 0; \partial F(y^+)) 
            \le \epsilon + \kappa\Vert y^+ - y\Vert. 
        \end{align*}
    \end{lemma}
    \begin{proof}
        Take it as a fact that the limiting subgradient of a weakly convex function is a closed bounded set. 
        Fix any $y$, there exists $w \in \partial \mathcal M(y^+; y)$ such that $\dist(\mathbf 0; \partial {\mathcal M}(y^+; y)) = \Vert w\Vert$ because $\partial M(\cdot;y)$ is a $\rho - \kappa$ weakly convex function. 
        Next, by definition we have
        \begin{align*}
            w &\in \partial F(y^+) + \kappa(y^+ - y)
            \\
            \iff 
            \exists v &
            \in \partial  F(y^+): 
            w = v + \kappa(y^+ - y)
            \\
            \implies 
            \epsilon &= 
            \Vert w\Vert = \Vert v + \kappa(y^+ - y)\Vert 
            \ge \Vert v\Vert - \Vert \kappa(y^+ - y)\Vert
            \\
            \implies 
            \dist(\mathbf 0, \partial F(y^+)) &\le 
            \Vert v\Vert 
            \le \epsilon + \Vert \kappa(y^+ - y)\Vert. 
        \end{align*}
